\documentclass[letterpaper,openany,oneside,twocolumn]{book}

\usepackage{fontspec}
\usepackage[justified]{dnd}
\usepackage{ifthen}
\usepackage{pstricks}

\usepackage[UKenglish]{babel}

\usepackage{dndtemplate}

\setlength\oddsidemargin{\dimexpr(\paperwidth-\textwidth)/2 - 1in\relax}
\setlength\evensidemargin{\oddsidemargin}

% Headline
\CharacterName{Elara}
\Class{Ranger 1}
\Background{Elven Ranger}
\PlayerName{Your Name}
\Race{Elf}
\Alignment{Neutral Good}
\XP{0}

% Ability scores
\StrengthScore{10}
\DexterityScore{16}
\ConstitutionScore{12}
\IntelligenceScore{12}
\WisdomScore{14}
\CharismaScore{10}

% Ability modifiers
\StrengthModifier{0}
\DexterityModifier{+3}
\ConstitutionModifier{+1}
\IntelligenceModifier{+1}
\WisdomModifier{+2}
\CharismaModifier{0}

% Saving Throws
\StrengthSavingThrowModifier{0}
\DexteritySavingThrowModifier{+3}
\ConstitutionSavingThrowModifier{+1}
\IntelligenceSavingThrowModifier{+1}
\WisdomSavingThrowModifier{+2}
\CharismaSavingThrowModifier{0}

\AcrobaticsSkillModifier{+3}
\AnimalHandlingSkillModifier{+2}
\ArcanaSkillModifier{+1}
\AthleticsSkillModifier{0}
\DeceptionSkillModifier{0}
\HistorySkillModifier{+1}
\InsightSkillModifier{+2}
\IntimidationSkillModifier{0}
\InvestigationSkillModifier{+1}
\MedicineSkillModifier{+2}
\NatureSkillModifier{+1}
\PerceptionSkillModifier{+4} % Proficient
\PerformanceSkillModifier{0}
\PersuasionSkillModifier{0}
\ReligionSkillModifier{+1}
\SleightOfHandSkillModifier{+3}
\StealthSkillModifier{+5} % Proficient
\SurvivalSkillModifier{+2}

% Proficiencies
\StrengthProficiency{}
\DexterityProficiency{True} % Ranger
\ConstitutionProficiency{}
\IntelligenceProficiency{}
\WisdomProficiency{}
\CharismaProficiency{}

\AcrobaticsProficiency{}
\AnimalHandlingProficiency{True} % Ranger
\ArcanaProficiency{}
\AthleticsProficiency{}
\DeceptionProficiency{}
\HistoryProficiency{}
\InsightProficiency{}
\IntimidationProficiency{}
\InvestigationProficiency{}
\MedicineProficiency{}
\NatureProficiency{True} % Ranger
\PerceptionProficiency{True} % Elf
\PerformanceProficiency{}
\PersuasionProficiency{}
\ReligionProficiency{}
\SleightOfHandProficiency{}
\StealthProficiency{True} % Ranger

\Inspiration{}
\Proficiency{+2}
\Perception{16}

\ArmorClass{15}
\Initiative{+3}
\Speed{30ft}
\MaxHitPoints{11}
\CurrentHitPoints{11}
\TemporaryHitPoints{}
\MaxHitDice{1d10}
\CurrentHitDice{1d10}

\CP{}
\SP{}
\GP{}
\EP{}
\PP{}

\
\AddWeapon{Longbow}{+5}{1d8+3 p}
\AddWeapon{Shortsword (x2)}{+5}{1d6+3 p}

\AttacksAdditional{
\textbf{Sharpshooter Feat:}\Attacking at long range doesn't impose disadvantage on your ranged weapon attack rolls. Your ranged weapon attacks ignore half cover and three-quarters cover. Before you make an attack with a ranged weapon that you are proficient with, you can choose to take a -5 penalty to the attack roll. If the attack hits, you add +10 to the attack's damage.\
}

\OtherProficienciesLanguages{
\textbf{Languages:}\Common, Elvish, Sylvan\
\textbf{Armor:}\Light armor, medium armor, shields\
\textbf{Weapons:}\Simple weapons, martial weapons\
}

\Equipment{
Longbow,
Quiver with 20 arrows,
Two shortswords,
Leather armor,
Dungeoneer's pack: backpack, crowbar, hammer, 10 pitons, 10 torches, tinderbox, 10 days of rations, waterskin, 50 feet of hempen rope,
Explorer's clothing,
Signet ring of the Elven Rangers
}

\PersonalityTraits{
    Curious: Elara has an insatiable curiosity about the world around her and is eager to learn about the different cultures and creatures of Elyndria.
    Empathetic: Elara has a strong connection to nature and its creatures, often sensing their emotions and needs.
}

\Ideals{
    Balance: Elara believes that maintaining balance in the natural world is vital for its survival, and she will do anything to protect it.
    Selflessness: Elara values the needs of others above her own, putting the well-being of Elyndria and its inhabitants before personal gain.}

\Bonds{
    The forests of Elyndria are her sanctuary, and she is fiercely protective of them.
    Elara is bound by duty to her fellow Elven Rangers, who share her commitment to maintaining balance in the natural world.
    }

\Flaws{
    Overprotective: Elara can be overly protective of her friends and allies, sometimes to the point of putting herself in harm's way.
    Stubborn: Once Elara has made up her mind, it's difficult to change her opinion, even if new evidence arises.}

\FeaturesTraits{
\textbf{Favored Enemy:}\Elementals. Advantage on Survival checks to track elementals and on Intelligence checks to recall information about them\
\textbf{Natural Explorer:}\Forest. When in forests, you have advantages on Intelligence and Wisdom checks related to terrain, and you're skilled at tracking creatures\
\textbf{Darkvision:}\60 feet\
\textbf{Keen Senses:}\Proficiency in Perception skill\
\textbf{Fey Ancestry:}\Advantage on saving throws against being charmed and magic can't put you to sleep\
\textbf{Trance:}\Elves don't need to sleep. Instead, they meditate deeply for 4 hours a day\
\textbf{Sharpshooter:}\You've mastered ranged weapons and can make shots that others find impossible. Attacking at long range doesn't impose disadvantage on your ranged weapon attack rolls. Your ranged weapon attacks ignore half cover and three-quarters cover. Before you make an attack with a ranged weapon that you are proficient with, you can choose to take a -5 penalty to the attack roll. If the attack hits, you add +10 to the attack's damage.
}

% Appearance

\Age{120}
\Height{5'6"}
\Weight{130lbs}
\Eyes{Emerald green}
\Skin{Fair with a slight golden hue}
\Hair{Auburn, waist-length, and usually braided}
\Scars{}
\UniqueFeatures{A delicate tattoo of intertwining vines and leaves encircles her right wrist, signifying her connection to the Elven Rangers.}

% Background

\CharacterAppearance{
Elara is a graceful and athletic elf, with well-defined muscles and a lithe build. Her eyes are a deep emerald green, expressing wisdom and empathy. Her fair skin has a slight golden hue, reminiscent of sun-dappled leaves. Elara's auburn hair falls in soft waves to her waist and is typically braided with small flowers and leaves as a symbol of her bond with nature.
}
\AdditionalFeaturesAndTraits{
Elara is an accomplished herbalist, skilled in creating potions and remedies to heal injuries and cure ailments. She has a keen sense of direction and a remarkable memory for details about her surroundings.
}
\Characterbackground{
Born and raised in the heart of Elyndria's lush forests, Elara was trained from a young age in the ways of the Elven Rangers. Under the tutelage of the elder ranger, Thalaniel, she learned to master the bow and blade while developing a deep connection to the natural world. Thalaniel recognized her innate talent for understanding the emotions and needs of the creatures around her and encouraged her to hone this ability. 
As Elara grew older, she became increasingly aware of the delicate balance that exists within the natural world and dedicated herself to preserving it. As an Elven Ranger, she was tasked with protecting the forests and its inhabitants from harm, whether it be from encroaching civilizations or malevolent forces. It was during her time as a ranger that Elara developed a particular affinity for battling elementals, driven by her desire to maintain harmony between the elements and the natural world.
}
\Treasure{
Elara possesses a beautifully crafted silver pendant in the shape of a leaf, which Thalaniel gifted to her upon her graduation from ranger training. The pendant holds a small reservoir of healing energy that can be used to restore vitality to herself or others.}
\AlliesAndOrganizations{
Elara is a respected member of the Elven Rangers, an organization dedicated to maintaining balance in the natural world and protecting the forests of Elyndria.}
\OrganizationName{The Elven Rangers
As a member of the Elven Rangers, Elara has formed close bonds with her fellow rangers, who share her commitment to protecting nature and maintaining balance in Elyndria. The organization is led by Thalaniel, a wise and powerful elf who has dedicated his life to understanding the secrets of the natural world. Under his guidance, the Elven Rangers have become a force to be reckoned with, able to quell threats to Elyndria's forests and wildlife.

The Elven Rangers are based in a hidden sanctuary deep within the forest, where they practice their skills and care for the creatures that inhabit the woodland realm. The sanctuary is protected by powerful wards that shield it from detection, ensuring that the rangers can continue their work undisturbed by outside forces.

As Elara embarks on her journey with Orlen to restore balance to the realm, she carries with her the knowledge and skills she has acquired as a member of the Elven Rangers. Her connection to nature, her empathetic understanding of creatures, and her dedication to the ideals of the Elven Rangers will guide her as she faces the challenges that lie ahead in the Elemental Nexus. Alongside Orlen, Elara hopes to discover the cause of the elemental imbalance and return harmony to Elyndria, fulfilling her duty as an Elven Ranger and honoring the legacy of her mentor, Thalaniel.
}

% Magic

\SpellcastingClass{Ranger}
\SpellcastingAbility{WIS}
\SpellSaveDC{12}
\SpellAttackBonus{+4}

\CantripSlotA{}
\CantripSlotB{}
\CantripSlotC{}

\end{document}

